Active Learning Benchmark

### 2023-01-31 doc/research_presentation/research_presentation.tex
presentation

\begin{frame}[fragile]{Hyperparameters}
	Data HPs are fixed for each dataset (budget, seed set, ...)

	Classifier HPs are set with BO per dataset (architecture, learning rate, regularization, ...)

	Environment HPs are choosen with respect to the classifiers (training loop, ...)

	Each AL agent defines its own state space with the information from the environment

	This leaves very few "true" hyperparameters: 
	\begin{itemize}
		\item Unlabeled Sample Size
		\item \# of cross validation trials
	\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Classifier Training}
	\begin{table}
		\centering
		\begin{tabular}{l || l}
			\textbf{General Setup} & \textbf{Speed Optimizations} \\
			\hline
			Cross-Entropy Loss & Fine tuning \\ [1mm]
			No case weights & Agressive Early Stopping \\[1mm]
			At least one epoch & \\[1mm]
			NAdam optimizer &
		\end{tabular}
	\end{table}
\end{frame}

@@

\begin{frame}[fragile]{Some Results}
	\begin{table}
		\centering
		\begin{tabular}{l || c | c }
			\textbf{Agent} & \textbf{Acc} & \textbf{AUC} \\
			\hline
			Oracle & 0.8806 $\pm$ 0.0141 & 0.8530 $\pm$ 0.0132 \\
			SAR & 0.8839 $\pm$ 0.0142 & 0.8339 $\pm$ 0.0118 \\
			Margin & 0.8849 $\pm$ 0.0112 & 0.8309 $\pm$ 0.0141 \\
			Entropy & 0.8822 $\pm$ 0.0156 & 0.8285 $\pm$ 0.0154 \\
			Coreset & 0.8788 $\pm$ 0.0105 & 0.8246 $\pm$ 0.0108 \\
			Random & 0.8744 $\pm$ 0.0144 & 0.8152 $\pm$ 0.0129
		\end{tabular}
		\caption*{Results for Splice}
	\end{table}
\end{frame}

>>>>

\begin{frame}[fragile]{Hyperparameters: Dataset}
	Budget is set to allow convergence

	Seed set is fixed to 1 point per class unless the cold start problem is to pronounced

	Classifier batch size / LR / regularization is optimized for performance \\
	Image datasets might require a trade-off for speed (Cifar10 currently needs 8 days)
\end{frame}

\begin{frame}[fragile]{Hyperparameters: Agent}
	Each AL agent defines its own state space with the information from the environment

	Other hyperparameters for baselines need to be investigated
\end{frame}

\begin{frame}[fragile]{True Hyperparameters}
	This leaves very few "true" hyperparameters: 
	\begin{itemize}
		\item Unlabeled Sample Size
		\item \# of cross validation trials
	\end{itemize}
\end{frame}

@@

\appendix

\begin{frame}[fragile]{Classifier Training}
	\begin{table}
		\centering
		\begin{tabular}{l || l}
			\textbf{General Setup} & \textbf{Speed Optimizations} \\
			\hline
			Cross-Entropy Loss & Fine tuning \\ [1mm]
			No case weights & Aggressive Early Stopping \\[1mm]
			At least one epoch & \\[1mm]
			NAdam optimizer &
		\end{tabular}
	\end{table}
\end{frame}

@@

\begin{frame}[fragile]{Results for Splice}
	\begin{table}
		\centering
		\begin{tabular}{l || c | c }
			\textbf{Agent} & \textbf{Acc} & \textbf{AUC} \\
			\hline
			Oracle & 0.8806 $\pm$ 0.0141 & 0.8530 $\pm$ 0.0132 \\
			SAR & 0.8839 $\pm$ 0.0142 & 0.8339 $\pm$ 0.0118 \\
			Margin & 0.8849 $\pm$ 0.0112 & 0.8309 $\pm$ 0.0141 \\
			Entropy & 0.8822 $\pm$ 0.0156 & 0.8285 $\pm$ 0.0154 \\
			Coreset & 0.8788 $\pm$ 0.0105 & 0.8246 $\pm$ 0.0108 \\
			Random & 0.8744 $\pm$ 0.0144 & 0.8152 $\pm$ 0.0129
		\end{tabular}
		\caption*{Results for Splice}
	\end{table}
\end{frame}
